Bird beak's elaboration and exploration: data preparation

### 2021-05-21 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

---
title: "Bird beak's elaboration and exploration: data preparation"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 8
    fig_height: 8
---

@@

@@

>>>>

---
title: "Bird beak's elaboration and exploration: data preparation"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
bibliography: references.bib
output:
  html_document:
    fig_width: 8
    fig_height: 8
---

All the custom code and custom functions called in this document can be downloaded and installed in `R` as the standalone working package `beer` (Beak Elaboration and Exploration in R).
Although `beer` is intentionally designed to be portable and shareable, we advice workers to use it with moderation and tailor it's consumption to their specific research needs.
The following code snippets are used to illustrate the implementation of the functions.
See §§§ for running the actual analyses.

```{r install_beer, eval = FALSE}
## Installing beer
devtools::install_github("TGuillerme/elaboration_exploration_bird_beaks/beer")
```

```{r load_beer, eval = TRUE}
## Loading beer
library(beer)

## Loading the demo data
data(demo_data)
data(demo_trees)
```

@@

TODO:

 * [ ] what's the data, where is it from
 * [ ] Procrustes
 * [ ] Building the trait space
   - [ ] form space version?
   - [ ] shape space version?
 * [ ] Clade data and grouping

Trees were manipulated in `R` [@Rcore] using the package `ape` [@ape].

@@

## Demo data

This is what the demo data looks like

```{r, plot_the_data}
## Plotting it
colour_vector <- c("orange", "blue", "darkgreen")
plot.space(demo_data,
           col = colour_vector,
           levels = demo_data$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC1 (6.86%)")
legend("topleft", legend = levels(demo_data$clade), col = colour_vector, pch = 19)
```

## References
